In-silico molecular enrichment and clearance of the human intracranial space

### 2024-11-28 paper/main.tex
Uncomment iffalse!

\section*{Introduction (rough ideas)}

@@

@@

PVS flow is important as shown by experimental studies. This is being
corroborated by clinical studies in humans (Eide and Ringstad (2024),
and the new one). However, a number of open questions remain: to what
extent do the PVS constitute an ensheathed space, how fast is the flow
in human PVS, what is the effect of dilated PVS as seen in disease
cases. Also, open questions on transport characteristics of the CSF
spaces - what gives the individual variations in tracer enhancements?

@@

\iffalse
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\mer{Update: ~2800 words and 7 subsections - around 300-450 words each?}
\begin{enumerate}
\item
  ``A digital twin'' for molecular enrichment and clearance in human intracranial spaces
\item
  CSF flow, the role of production versus no/cardiac/respiratory
  dispersive effects on tracer trajectories, flow bifurcation. With and without tentorium cerebellum.
\item
  ``The role'' of PVS flow speed
\item
  ``The role'' of PVS sheaths and permeability - does functional separation entail structural separation?
\item
  ``The role'' of PVS size (motivated by pathologies)
\item
  Clearance from the CSF spaces - with and without low pressure veins, but keeping the intrathecal source of solute. 
\item
  Clearance from the parenchyma: $c_0 = 1.0$. Different substances?
\end{enumerate}

@@

\fi

@@

\iffalse
\newpage
\section*{Acknowledgments (not compulsory)}

>>>>

@@

% What we already know about the problem

% What are our research questions and how do we answer them

% Main findings and outlook

\newpage
\section*{Introduction (rough ideas)}

\begin{itemize}
\item
  Need better understanding of transport of solutes in intracranial spaces.
\item
  Need to integrate separate observations e.g. on diffusion in
  neuropil, PVS flow, net flow, effect of dispersion
\item
 Need to transfer and integrate insights from animal models,
  computational models and theoretical insights into the human case. 
\item
 Controversies need to be resolved.
\end{itemize}

@@

PVS flow is important as shown by experimental studies. This is being
corroborated by clinical studies in humans (Eide and Ringstad (2024),
and the new one). However, a number of open questions remain: to what
extent are PVSs compartmentalized, how fast is the flow in human PVS,
what is the effect of dilated PVS as seen in disease cases etc.  Also,
open questions on transport characteristics of the CSF spaces - what
gives the individual variations in tracer enhancements?

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\mer{Update: ~2800 words and 7 subsections - around 300-450 words each?}
\begin{enumerate}
\item
  ``A digital twin'' for molecular enrichment and clearance in human intracranial spaces
\item
  CSF flow, the role of production versus no/cardiac/respiratory
  dispersive effects on tracer trajectories, flow bifurcation. With and without tentorium cerebellum.
\item
  ``The role'' of PVS flow speed
\item
  ``The role'' of PVS sheaths and permeability - does functional separation entail structural separation?
\item
  ``The role'' of PVS size (motivated by pathologies)
\item
  Clearance from the CSF spaces - with and without low pressure veins, but keeping the intrathecal source of solute. 
\item
  Clearance from the parenchyma: $c_0 = 1.0$. Different substances?
\end{enumerate}

@@

@@

\newpage
\section*{Acknowledgments (not compulsory)}
